\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-21 paper.qmd
Changed notations

Let $g : \mathbb{R}^{n\times k} \rightarrow \mathbb{R}^{m\times k}$ be the function that maps a point in \kD{} space to it's bin centroid ($C^{(k)}$). This is the model points in \kD{} space.

@@

with corresponding \pD{} vector $\vec{f_i}$. Then, $f(g(x))$ maps a \pD{} point to the \pD{} model estimate, completing the model cycle.

>>>>

Let $u : \mathbb{R}^{n\times k} \rightarrow \mathbb{R}^{m\times k}$ be the function that maps a point in \kD{} space to it's bin centroid ($C^{(k)}$). This is the model points in \kD{} space.

@@

with corresponding \pD{} vector $\vec{f_i}$. Then, $f(u(x))$ maps a \pD{} point to the \pD{} model estimate, completing the model cycle.

### 2024-05-21 paper.tex
Changed notations

Let \(g : \mathbb{R}^{n\times k} \rightarrow \mathbb{R}^{m\times k}\) be
the function that maps a point in \kD{} space to it's bin centroid
(\(C^{(k)}\)). This is the model points in \kD{} space.

@@

with corresponding \pD{} vector \(\vec{f_i}\). Then, \(f(g(x))\) maps a
\pD{} point to the \pD{} model estimate, completing the model cycle.

>>>>

Let \(u : \mathbb{R}^{n\times k} \rightarrow \mathbb{R}^{m\times k}\) be
the function that maps a point in \kD{} space to it's bin centroid
(\(C^{(k)}\)). This is the model points in \kD{} space.

@@

with corresponding \pD{} vector \(\vec{f_i}\). Then, \(f(u(x))\) maps a
\pD{} point to the \pD{} model estimate, completing the model cycle.
